A simulation model of DNA methylation data

### 2015-05-05 Rmarkdown/methsim.Rmd
Knocking off TODOs
Add y-axis label to boxplots of beta by region

\begin{figure}[!htb]
\centering
\centering
\includegraphics[width=\textwidth]{../figures/Seisenberger_beta_by_pm_boxplots.pdf}
\caption[\emph{Seisenberger}: $\beta$-values by region-type]{Boxplots of CpG $\beta$-values in each region-type following segmentation by \texttt{MethylSeekR} for the \emph{Seisenberger} dataset.}
\label{fig:Seisenberger_beta_by_pm_boxplots}
\end{figure}

@@

While `methsim` is an R package, much of it is written in \CC, using the Rcpp package \citep{Eddelbuettel:2011to, Eddelbuettel:2013if}, which greatly speeds up the running time of key procedures. Furthermore, several steps of the simulation can be run in parallel for each chromosome. Parallelism is implemented via the `BiocParallel` Bioconductor package \citep{BiocParallel}.

>>>>

\begin{figure}[!htb]
\centering
\centering
\includegraphics[width=\textwidth]{../figures/Seisenberger_beta_by_pm_boxplots.pdf}
\caption[\emph{Seisenberger}: $\beta$-values by region-type]{Boxplots of CpG $\beta$-values in each region-type following segmentation by \texttt{MethylSeekR} for the \emph{Seisenberger} dataset. \texttt{MethylSeekR} was unable to partition the \emph{E16.5\_male\_1} methylome due to its unusual $\beta$-value distribution, hence no data is shown for this sample.}
\label{fig:Seisenberger_beta_by_pm_boxplots}
\end{figure}

@@

While `methsim` is an R package, much of it is written in \CC, using the Rcpp package \citep{Eddelbuettel:2011to, Eddelbuettel:2013if}, which greatly speeds up the running time of key procedures. Furthermore, several steps of the simulation can be run in parallel for each chromosome. Parallelism is implemented via the `BiocParallel` Bioconductor package (\url{http://bioconductor.org/packages/BiocParallel}).
